|

### 2019-06-10 inst/manuscript/manuscript.Rmd
Combine golgi, ER, vacuole proteins in table 1
Also:
 - Fix protein names in figure 8 so they are not in all
   capitals.
 - Separate Vac8 and Ykt6 in figure 8

# add proper protein functions to table 1
# also add vesicle depleted supernatant info and 
# group proteins according to localisation
marker_longlist <- marker_longlist %>% 
  mutate(Function = function_desc1, 
         VDM = c("Y", rep("",3), rep("Y", 2), "", "Y", rep("", 8), rep("Y", 2), 
                 rep("", 4), rep("Y", 3), rep("", 2), rep("Y", 2), rep("", 5), 
                 "Y", rep("", 7), "Y"), 
         pack_row = c(5, rep(1,3), rep(5,2), 1, 2, rep(1,3), rep(1,3), 4, 2, 
                      rep(5,2), 1, rep(2,2), 4, 1, rep(5,2), 1, rep(5,3), 1, 
                      4, rep(1,3), 5, 1, 1, 3, 1, 3, 2, 3, 5)) %>% 
  arrange(pack_row)

@@

# draw table 1
knitr::kable(marker_longlist[ ,-10],
             caption = tab1_cap, 
             format = "latex", 
             booktabs = TRUE, 
             longtable = TRUE, 
             linesep = "", 
             escape = FALSE)  %>% 
  row_spec(row = c(1, 5, 6, 11, 12, 15:20, 22:27, 39), underline = TRUE) %>% 
  add_header_above(c(" " = 2, 
                     "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
                     " " = 2), escape = FALSE) %>% 
  kable_styling(font_size = 8) %>% 
  pack_rows("Plasma membrane", 1, 20) %>% 
  pack_rows("Golgi, ER, secretory pathway", 21, 25) %>% 
  pack_rows("Vacuole", 26, 28) %>% 
  pack_rows("Mitochondria", 29, 31) %>% 
  pack_rows("Cell wall, cell surface", 32, 43) %>% 
  footnote(alphabet = c("Protein localisation was inferred from sequence 
                         similarity with \\\\textit{S. cerevisiae} ortholog as 
                         annotated in the Candida Genome Database 
                        (ref:footnote1)", 
                        "Protein localisation was predicted using DeepLoc-1.0 
                        (ref:footnote2)", 
                        "Presence of transmembrane domains and absense of a 
                        signal peptide was predicted using TOPCONS2 
                        (ref:footnote3)"), 
           escape = FALSE, 
           threeparttable = TRUE)
```

>>>>

# add proper protein functions to table 1
# also add vesicle depleted supernatant info and 
# group proteins according to localisation
marker_longlist <- marker_longlist %>% 
  mutate(Function = function_desc1, 
         VDM = c("Y", rep("",3), rep("Y", 2), "", "Y", rep("", 8), rep("Y", 2), 
                 rep("", 4), rep("Y", 3), rep("", 2), rep("Y", 2), rep("", 5), 
                 "Y", rep("", 7), "Y"), 
         pack_row = c(4, rep(1,3), rep(4,2), 1, 2, rep(1,3), rep(1,3), 3, 2, 
                      rep(4,2), 1, rep(2,2), 3, 1, rep(4,2), 1, rep(4,3), 1, 
                      3, rep(1,3), 4, 1, 1, 2, 1, 2, 2, 2, 4)) %>% 
  arrange(pack_row)

@@

# draw table 1
knitr::kable(marker_longlist[ ,-10],
             caption = tab1_cap, 
             format = "latex", 
             booktabs = TRUE, 
             longtable = TRUE, 
             linesep = "", 
             escape = FALSE)  %>% 
  row_spec(row = c(1, 5, 6, 11, 12, 15:20, 22:27, 39), underline = TRUE) %>% 
  add_header_above(c(" " = 2, 
                     "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
                     " " = 2), escape = FALSE) %>% 
  kable_styling(font_size = 8) %>% 
  pack_rows("Plasma membrane", 1, 20) %>% 
  pack_rows("Golgi, ER, vacuole", 21, 28) %>% 
  pack_rows("Mitochondria", 29, 31) %>% 
  pack_rows("Cell wall, cell surface", 32, 43) %>% 
  footnote(alphabet = c("Protein localisation was inferred from sequence 
                         similarity with \\\\textit{S. cerevisiae} ortholog as 
                         annotated in the Candida Genome Database 
                        (ref:footnote1)", 
                        "Protein localisation was predicted using DeepLoc-1.0 
                        (ref:footnote2)", 
                        "Presence of transmembrane domains and absense of a 
                        signal peptide was predicted using TOPCONS2 
                        (ref:footnote3)"), 
           escape = FALSE, 
           threeparttable = TRUE)
```
